\documentclass{sig-alternate-05-2015}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{svg}
\usepackage{url}
\usepackage{amsmath}
\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


\title{SmartPhone based Sound Direction Estimation}

%

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Amit Sharma, Youngki Lee, Rajesh K Balan, Archan Misra\\     
       \affaddr{Singapore Management University}\\
       \affaddr{Singapore}\\
       \email{\{amit.2015, youngkilee, rajesh, archanm\}@smu.edu.sg}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.




% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Information about sound direction can be quite useful in certain situations. For example, imagine a lecture hall with video recording facility. We want to video record the speaker along with attendants asking questions, if any. Using a smartphone, we can detect direction of current speaker and accordingly automatically rotate the camera to capture the speaker. Another application could be assistance to a deaf person in a meeting. Since they rely on lip/gesture reading of the speaker to understand the ongoing discussion, so a smartphone can be used to detect the speaker direction and help the deaf person look in appropriate direction.\\

In this work, we present our sound direction estimation application that exploits Time Difference of Arrival (TDOA) of two signals at two microphones of a smartphone and signal cross-correlation for angle estimation. We used only one smartphone with two microphones to detect directions from 0 to 180 degrees. Experiment results for using \textit{white noise} as a sound source are discussed in this work. Our approach can detect 37 different angles for a smartphone with microphones 14 cm from each other.

\end{abstract}


\keywords{SmartPhone, Time-differnce of Arrival (TDOA), Angle of Arrival, Cross-Correlation}

\input{introduction}


%\section{Related work}

\input{system_design}

\input{experiments}

\section{Results}

\input{future_work}

\nocite{4459286}
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{biblio}  % sigproc.bib is the name of the Bibliography in this case

% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns

\end{document}
